Chapter 2 Draft

### 2020-04-02 Rmd/Draft.Rmd
preparing metadata and now organizing networks

---
title: "Draft"
output:
  pdf_document: default
  html_document: default
fontsize: 12pt
header-includes:
    - \usepackage{setspace}\doublespacing
bibliography: [references.bib]
---
Here I'm going to try to understand our data a bit better and state our hypothesis.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center'}
setwd("~/R_Projects/Reproductive Traits")

>>>>

---
title: "Chapter 2 Draft"
output:
  pdf_document: default
  html_document: default
fontsize: 12pt
header-includes:
    - \usepackage{setspace}\doublespacing
bibliography: [references.bib]
---
Here I'm going to try to understand our data a bit better and state our hypothesis.

@@

\vspace{4cm}

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.align='center', fig.width=10,fig.height=7}
setwd("~/R_Projects/Reproductive Traits")
